WTCIII-Figures

### 2015-07-06 markdown/WTC3_figures.Rmd
added tobacco dataframes to testing script

#### <u>Design</u>
* WTCIII was a warming experiment with ambient and +3°C warming (n=6).  A drought manipulation was added in the last few months of the experiment but is not included here.
* Sun leaves were measured in the upper canopy at their current PPFD.  Shade leaves were measured in the lower/middle canopy, first at their current PPFD and then again at sun leaf PPFD as a simulated sunfleck.
* New fully expanded leaves were measured. Shade leaves were sampled into the middle canopy as the experiment progressed to avoid issues with leaf age.
* Leaf physiological measurements were taken at their current temperature (ambient, +3°C). Thus, data below represent a large range of temperatures from 18-35°C.

>>>>

#### <u>Design</u>
* WTCIII was a warming experiment with ambient and +3°C warming (n=6).  A drought manipulation was added in the last few months of the experiment but is not included here.
* Sun leaves were measured in the upper canopy at their current PPFD.  Shade leaves were measured in the lower/middle canopy, first at their current PPFD and then again at sun leaf PPFD as a simulated sunfleck (Shade-Low light & Shade-High light).
* New fully expanded leaves were measured. Shade leaves were sampled into the middle canopy as the experiment progressed to avoid issues with leaf age.
* Leaf physiological measurements were taken at their current temperature (ambient, +3°C). Thus, data below represent a large range of temperatures from 18-35°C.
